Evolving New State-of-the-Art for Voronoi Diagram and Distance Transform From JFA Using AutoML

### 2020-09-19 paper/main.tex
"automl" section

The original author of JFA\footnote{Guodong Rong} defined some variants and
modifications \citep{rong2007variants}, in this work we continue on this subject
and examine the relationship between them.

@@

\hl{przeniesc do Proposed Method}

\url{https://arxiv.org/pdf/1801.09373.pdf}
\url{https://arxiv.org/pdf/1804.10120.pdf}
\url{https://arxiv.org/pdf/1703.06353.pdf}

okay przenioslem - dodac prace co tez tak szuka algosow

>>>>

The original author of JFA\footnote{Guodong Rong} defined some variants and
modifications \citep{rong2007variants}, in this work we continue on this subject
and examine the relationship between them.
We chose this algorithm because it is the simplest to implement and it has a wide variety of improvements.

% We choose this variant because it's the simplest and have wide range of improvements to apply.

@@

% FIXME:
% --> "DEEPCODER: LEARNING TO WRITE PROGRAMS"
%      https://arxiv.org/pdf/1611.01989.pdf
% --> "Deep Learning for Source Code Modeling and Generation:
%                                 Models, Applications and Challenges"
%      https://arxiv.org/pdf/2002.05442.pdf
% --> "Selecting Representative Examples for Program Synthesis"
%      https://arxiv.org/pdf/1711.03243.pdf
% --> "Enhancing Dynamic Symbolic Execution by
%             Automatically Learning Search Heuristics"
%      https://arxiv.org/pdf/1907.09700.pdf

Program synthesis is a class of regression problems where one seeks a solution,
in the form of a source-code program, mapping the inputs to their corresponding
outputs errorless \citep{pu2018selecting}.  If we have a broad range of
acceptable solutions, another aspect is how efficient the produced code is.

There are two key ingredients to a synthesis problem: a domain specific language
(DSL for short) and a specification. The DSL defines a space of candidate
programs which serve as the model class. DSL-based models create different
grammar rules for common code statements (e.g., control flow, comments, and
brackets).  The specification is commonly expressed as a set of input-output
examples which the candidate program needs to fit exactly. In our problem, these
examples are produced by bruteforce algorithm.

Given the precise and combinatorial nature of synthesis, gradient-descent based
approaches perform poorly and an explicit search over the solution space is
required \citep{balog2016deepcoder}.

% https://arxiv.org/pdf/1611.01989.pdf

% Another factor is how efficient the generated code is if we have wide range
% acceptable solution.

% [FIXME]
% \hl{nie wiem jak opisac to ze generujemy kody ze slownika, definiujemy sobie
% jakies punkty i szukamy najlepszego w danej dziedzinie - NAJlepsze ze w tej
% sekcji powinnismy to zrobic bez naszego approchu - tylko patrzcie TEN pan to juz
% robil przed nami - zrobimy podobnie}

% chlip: https://www.youtube.com/watch?v=Azf0BVBrJ0c&t=0s

% Selecting Representative Examples for Program Synthesis
% \url{https://arxiv.org/pdf/1711.03243.pdf}

% Deep Learning for Source Code Modeling and Generation:
%  Models, Applications and Challenges
%\url{https://arxiv.org/pdf/2002.05442.pdf}

% CEL: automl-zero zdefiniowalo operacje i budowalo kod
%      my zrobimy cos jak DSL na voronoi-a implementujac jako opcje rozne
%      modyfikacje (np. typ anchoru)

% Domain-specific languages (DSLs) are often used to define the parametrization
% rules and states for generating the structure of a program. DSL-based models
% create different grammar rules for common code statements (e.g., control flow,
% comments, and brackets). Compared to a general purpose programming language, the
% grammar size of a DSL is usually smaller, which makes it more efficient for
% specific code generation tasks.

% Our solution will use \textit{program template}.

% \url{https://arxiv.org/pdf/1801.09373.pdf}
% \url{https://arxiv.org/pdf/1804.10120.pdf}
% \url{https://arxiv.org/pdf/1703.06353.pdf}

% [TAGS]
% SOURCE CODE MODELING
% MuZero
% program synthesis
% Selecting representative examples for program synthesis
